Supplement: A Continuous Occlusion Model for Road Scene Understanding

### 2016-03-28 CVPR16/Source/experiments2.tex
Addressed other comments from R24. (1) Added one of the references (2) take -> taken (3) Explained how we get the number of cars from detections (4) Added statistics about KITTI dataset (5) Clarified that we use Song and Chandrakar 2014 for initializing 3D location and sizes as well. (6) Added baselines to experiment table (7) Added one line explanation of the baselines (8) Clarified the Lambertian reflection line (9) summer -> sum

In this section, we benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010}. We then show how the proposed model may be applied for 3D localization in road scenes. For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions. 
%It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

@@

For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively. We then apply \cite{Zach2007} to extract point tracks. Note that our method can handle occlusions in both static and dynamic scenes, but motion segmentation focuses on dynamic scenes. For a complete evaluation, we organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks. In addition to point tracks, the parameters of all objects (cars) estimated by the method of \cite{Song_Chandraker_2015} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).

@@

\begin{table}
  \begin{tabular}{lrr}
    \toprule
    Energy & t & dim \\
    \midrule
    $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
    & 3.95  & 1.72\\        
    $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
    & 4.81  & 2.16\\        
    $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
    & 4.05  & {\bf 1.59}\\        
    $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
    & {\bf 3.24}  & 2.16\\
    \bottomrule
  \end{tabular}
  \caption{\small Localization experiment results with different combinations of energies. We report translation error (t) and dimension error (dim) in meters per car. Yaw angles for static objects are not optimized by our model. These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
  \label{tab:localizationExperiment}
\end{table}

\subsection{Localization Experiments}
We report errors in translation and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}. Average depth of cars in the dataset is approximately $20$ meters. We compare four combinations of energies.  The energy $\EnergyTrackNoOcc$ represents the point tracks energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the modification of $\Lambda_k$ that accounts for occlusion. We observe that the use of the continuous occlusion model improves the localization accuracy in terms of the translation error, which is the most significant metric affected by all cues. Occlusion modeling for detection increases dimension error since we explicitly allow greater uncertainty in occluded edges of the bounding box. Note that none of our energies optimize yaw angles for static objects, which can be handled in practice through either the detector orientation or external information such as lane geometry.

>>>>

In this section, we benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010}. We then show how the proposed model may be applied for 3D localization in road scenes. For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of 35 video sequences (10088 frames, 634 object tracks) of road scenes under a variety of driving conditions. 
%It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

@@

For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively. We then apply \cite{Zach2007} to extract point tracks. Note that our method can handle occlusions in both static and dynamic scenes, but motion segmentation focuses on dynamic scenes. For a complete evaluation, we organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks. In addition to point tracks, the parameters of all objects (cars)--including their unknown 3D position and sizes--estimated by the method of \cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).

@@

\begin{table}
  \begin{tabular}{lrr}
    \toprule
    Method & t & dim \\
    \midrule
    Point cloud fit
    & 6.87 & 4.02\\
    Initialization
    & 5.61 & 3.23\\
    $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
    & 3.95  & 1.72\\        
    $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
    & 4.81  & 2.16\\        
    $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
    & 4.05  & {\bf 1.59}\\        
    $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
    & {\bf 3.24}  & 2.16\\
    \bottomrule
  \end{tabular}
  \caption{\small Localization experiment results with different combinations of energies. We report translation error (t) and dimension error (dim) in meters per car. Yaw angles for static objects are not optimized by our model. These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
  \label{tab:localizationExperiment}
\end{table}

\subsection{Localization Experiments}
We report errors in translation and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}. Average depth of cars in the dataset is approximately $20$ meters. We compare four combinations of energies with two baselines. We initialize the unknowns using \cite{Song_Chandraker_2014} whose accuracy is reported as \emph{Initialization} in the table. We develop a simple baseline by fitting cuboids to the point cloud created by triangulation of point tracks in two successive frames. The accuracy of this baseline is reported as \emph{Point cloud fit} in the table. The energy $\EnergyTrackNoOcc$ represents the point tracks energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the modification of $\Lambda_k$ that accounts for occlusion. We observe that the use of the continuous occlusion model improves the localization accuracy in terms of the translation error, which is the most significant metric affected by all cues. Occlusion modeling for detection increases dimension error since we explicitly allow greater uncertainty in occluded edges of the bounding box. Note that none of our energies optimize yaw angles for static objects, which can be handled in practice through either the detector orientation or external information such as lane geometry.

### 2016-03-28 CVPR16/Source/occlusion.tex
Addressed other comments from R24. (1) Added one of the references (2) take -> taken (3) Explained how we get the number of cars from detections (4) Added statistics about KITTI dataset (5) Clarified that we use Song and Chandrakar 2014 for initializing 3D location and sizes as well. (6) Added baselines to experiment table (7) Added one line explanation of the baselines (8) Clarified the Lambertian reflection line (9) summer -> sum

\vspace{-0.3cm}
\paragraph{Reflection probability}
Consider a 3D point $\bx_j$ observed in the image at pixel $\bu_j$. Let $\bK$ be the intrinsic calibration matrix for the camera and $\ray = \displaystyle\frac{\bK^{-1}\bu_j}{\lVert \bK^{-1}\bu_j \rVert}$ be the unit vector along the backprojected ray from the camera center passing through $\bu_j$. Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the gradient of the object's occupancy function $f_{occ}^i$:%
\begin{align}
   \Prefl = \frac{1}{\Zrefl}(\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2
\label{eq:evalPrefl}
\end{align}
The $\max \{ \}$ ensures that the negative probability due to gradient in the direction opposite to the ray is clipped off and squaring the function allows it to be smooth near zero. We note that in the extreme case of an object being Lambertian, the above reverts to a (squared) Lambertian reflection. The $\Zrefl$ denotes the normalization factor such that $\int_{0^+}^\infty \Prefl d\lambda = 1$.

\vspace{-0.3cm}
\paragraph{Transmission probability}
\label{sec:ptransmission}
Since we are modeling occupancy as transparency, we derive inspiration from optics for the modeling of translucent objects. A model for transmission of light across a distance $\alpha$, through a medium of density $\rho$ and opacity $\beta$ is given by the Beer-Lambert Law:
\begin{align}
I(\alpha) = I_0 e^{-\beta\rho\alpha}.
\end{align}
%
In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function summer over all objects, $\occftot = \sum_i \occf$. Further, the domain of our ocupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$. Thus, we replace $e^{-\beta\rho}$ by the transparency function $1 - \occftot$ and consequently, the transmission probability over a small distance $d\lambda$ is given by
%
\begin{align}
  \!\!\!\! P^j_{\textit{transmission}}(\lambda + d\lambda) = P^j_{\textit{transmission}}(\lambda) (1-\occftot)^{d\lambda}.
\end{align}
%
Thus, for an image point $\bu_j$ to correspond to a 3D point $\bx_j$ at depth $\lambda$ along the backprojected ray $\ray$, the ray must be transmitted through space with the probability
\begin{align}
P^j_{\textit{transmission}}(\lambda) = \prod_{c}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda}.
\label{eq:ptrans-integral}
\end{align}
Here, $\prod_{c}^{\lambda}$ represents a \emph{product integral} from $c$ to $\lambda$, where $c$ is the position of camera screen, considered here to be equivalent to the focal length of the camera .\footnote{A product integral is a simple integral in the log domain: 
\vspace{-0.2cm}
\begin{equation}
\prod_{c}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} = e^{\int_{c}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}. \nonumber
\end{equation}
}

>>>>

\vspace{-0.3cm}
\paragraph{Reflection probability}
Consider a 3D point $\bx_j$ observed in the image at pixel $\bu_j$. Let $\bK$ be the intrinsic calibration matrix for the camera and $\ray = \displaystyle\frac{\bK^{-1}\bu_j}{\lVert \bK^{-1}\bu_j \rVert}$ be the unit vector along the backprojected ray from the camera center passing through $\bu_j$. Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the gradient of the object's occupancy function $f_{occ}^i$:%
\begin{align}
   \Prefl = \frac{1}{\Zrefl}(\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2
\label{eq:evalPrefl}
\end{align}
The $\max \{ \}$ ensures that the negative probability due to gradient in the direction opposite to the ray is clipped off and squaring the function allows it to be smooth near zero. We note that in the extreme case of an object being fully opaque (i.e. $\nabla {f^i_{occ}(\bx_j)} \in \{0,1\}$), the above model reverts to a (squared) Lambertian reflection. The $\Zrefl$ denotes the normalization factor such that $\int_{0^+}^\infty \Prefl d\lambda = 1$.

\vspace{-0.3cm}
\paragraph{Transmission probability}
\label{sec:ptransmission}
Since we are modeling occupancy as transparency, we derive inspiration from optics for the modeling of translucent objects. A model for transmission of light across a distance $\alpha$, through a medium of density $\rho$ and opacity $\beta$ is given by the Beer-Lambert Law:
\begin{align}
I(\alpha) = I_0 e^{-\beta\rho\alpha}.
\end{align}
%
In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function sum over all objects, $\occftot = \sum_i \occf$. Further, the domain of our ocupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$. Thus, we replace $e^{-\beta\rho}$ by the transparency function $1 - \occftot$ and consequently, the transmission probability over a small distance $d\lambda$ is given by
%
\begin{align}
  \!\!\!\! P^j_{\textit{transmission}}(\lambda + d\lambda) = P^j_{\textit{transmission}}(\lambda) (1-\occftot)^{d\lambda}.
\end{align}
%
Thus, for an image point $\bu_j$ to correspond to a 3D point $\bx_j$ at depth $\lambda$ along the backprojected ray $\ray$, the ray must be transmitted through space with the probability
\begin{align}
P^j_{\textit{transmission}}(\lambda) = \prod_{c}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda}.
\label{eq:ptrans-integral}
\end{align}
Here, $\prod_{c}^{\lambda}$ represents a \emph{product integral} from $c$ to $\lambda$, where $c$ is the position of camera screen, considered here to be equivalent to the focal length of the camera .\footnote{A product integral is a simple integral in the log domain: 
\vspace{-0.2cm}
\begin{equation}
\prod_{c}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} = e^{\int_{c}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}. \nonumber
\end{equation}
}

### 2016-03-28 CVPR16/Source/related.tex
Addressed other comments from R24. (1) Added one of the references (2) take -> taken (3) Explained how we get the number of cars from detections (4) Added statistics about KITTI dataset (5) Clarified that we use Song and Chandrakar 2014 for initializing 3D location and sizes as well. (6) Added baselines to experiment table (7) Added one line explanation of the baselines (8) Clarified the Lambertian reflection line (9) summer -> sum

>>>>

One of the models closest to our unified occupancy model was recently presented by Rhodin et al. \cite{Rhodin:2015} applied to the problem of pose estimation.  Although they model transmission probability like we do, they do not model reflectance probability. We explicitly model reflectance probability that differentiates between the center and surface of the 3D object.
